---
title: "How many packages are there on CRAN?"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

This shows one how to scrape data directly from a website `r emo::ji("spider_web")` (an html table of CRAN packages, structure it as a dataframe and plot it).

>Loads R packages `r emo::ji("package")` 

```{r setup,message=F}
library(tidyverse)
library(ggthemes)
library(lubridate)
library(hash)
library(tictoc)
```

>Loads functionality to decode and plot CRAN data `r emo::ji("computer")`

```{r}
source("count_cran.R")
```

>Reads package table (as html) from CRAN and decode it into a dataframe: `r emo::ji("man_technologist")`

```{r,cache=T}
url_cran <- "http://cran.r-project.org/web/packages/available_packages_by_date.html"
df_cran <- read_file(url_cran) %>% cran_html_to_df
nrow(df_cran)
```

What's in it?

```{r}
glimpse(df_cran)
```

>What are the top 10 words used in package titles?

```{r}
df_cran %>%
  get_top_words(10) %>%
  plot_top_words
```

>Plots it! `r emo::ji("chart")` 

```{r}
df_cran %>%
  plot_cran_df +
  theme_economist()
```

>There you have it! R is growing exponentially!`r emo::ji("smile")`